Evaluation of classical correlation functions from 2/3D images on CPU and GPU architectures: introducing CorrelationFunctions.jl

### 2023-04-28 paper-correlations.tex
Remove unused appendix
Update an algorithm for L₂

@@

\begin{algorithmic}[1]
  \Procedure{countruns}{$a, len, phase$}
    \State $runslist \gets [\quad]$
    \State $runs \gets 0$
    \ForAll{$x \in a$}
      \If{$x = phase$}
        \State $runs \gets runs + 1$
      \ElsIf{$runs \ne 0$}
        \State $runslist \gets runs:runslist$
        \State $runs \gets 0$
      \EndIf
    \EndFor
    \If{$runs \ne 0$}
      \State $runslist \gets runs:runslist$
    \EndIf
    \State \textbf{return} $runslist$
  \EndProcedure
  \\
  \Procedure{updateruns}{$a, runs, n$}
    \For{$idx = 1,n$}
      \State $a[idx] \gets a[idx] + runs$
      \State $runs \gets runs - 1$
    \EndFor
  \EndProcedure
  \\
  \Procedure{updateperiodic}{$a, first, last, n$}
    \State $sum \gets first + last$
    \State $n \gets \min(n, sum)$
    \For{$idx = 1,n$}
      \State $a \gets \min(idx - 1, first, last, sum - (idx - 1))$
      \State $a[idx] \gets a[idx] + a$
    \EndFor
  \EndProcedure
  \\
  \Procedure{l2}{$a, phase, maxlen, periodic$}
    \State $success \gets zeros(maxlen)$
    \State $total \gets zeros(maxlen)$
    \State $len \gets length(a)$
    \State $nupdates \gets \min(len, maxlen)$
    \State $runs \gets countruns(a, maxlen, phase)$
    \ForAll{$run \in runs$}
      \State $updateruns(success, run, \min(run, maxlen))$
    \EndFor
    \If{$periodic$}
      \State $first \gets first(a)$
      \State $last \gets last(a)$
      \If{$first = last$}
        \State $updateperiodic(success, first, last, nupdates)$
      \EndIf
      \State Increment $total[\text{from} \, 1 \, \text{to} \, nupdates]$ by
      $len$
    \Else
      \State $updateruns(total, len, nupdates)$
    \EndIf
    \State \textbf{return} $success$ divided by $total$ element-wise.  
  \EndProcedure
\end{algorithmic}

\section{Algorithm for image rotation}
\label{rotating}

\begin{algorithmic}[1]
  \Procedure{rotate}{$a, direction, periodic$}
    \ForAll{$slice \in eachslice(a)$}
      \State $shift \gets get\_shift(slice, direction)$
      \State $rotated\_slice \gets circshift(slice, shift)$
      \If{$! periodic$}
        \State $rotated\_slice[end - shift:end] \gets -1$
      \EndIf
    \EndFor
  \State \textbf{return} $rotated$
  \EndProcedure
\end{algorithmic}

>>>>

An algorithm for computation of linear-path function for one-dimensional slice
is present below. Here $a$ is a one-dimensional input array, $phase$ can be
void, solid or some other phase, and $periodic$ is a boolean value which equals
to true if we compute $L_2$ in periodic mode and false otherwise. The efficiency
of the proposed algorithm is $O(n)$ where $n$ is the length of the array.
\begin{algorithmic}[1]
  \Procedure{l2}{$a, phase, periodic$}
    \State $len \gets length(a)$
    \State $result \gets zeros(len)$
    \State $runs \gets countruns(a, phase)$
    \ForAll{$run \in runs$}
      \State $updateruns(result, run)$
    \EndFor
    \If{$periodic$}
      \State $first \gets first(a)$
      \State $last \gets last(a)$
      \If{$first = last$}
        \State $updateperiodic(result, first, last)$
      \EndIf
    \EndIf
    \State \textbf{return} $success$ divided by number of trials
    (see \cref{sec:number-of-trials})
  \EndProcedure
  \\
  \Procedure{countruns}{$a, phase$}
    \State $runslist \gets [\ ]$
    \State $runs \gets 0$
    \ForAll{$x \in a$}
      \If{$x = phase$}
        \State $runs \gets runs + 1$
      \ElsIf{$runs \ne 0$}
        \Comment Add $runs$ to the accumulator
        \State $runslist \gets runs:runslist$
        \State $runs \gets 0$
      \EndIf
    \EndFor
    \If{$runs \ne 0$}
      \State $runslist \gets runs:runslist$
    \EndIf
    \State \textbf{return} $runslist$
  \EndProcedure
  \\
  \Procedure{updateruns}{$array, runs$}
    \State $r \gets runs$
    \For{$idx = 0,\ idx < runs$}
      \State $array[idx] \gets array[idx] + r$
      \State $r \gets r - 1$
    \EndFor
  \EndProcedure
  \\
  \Procedure{updateperiodic}{$a, first, last$}
    \State $sum \gets first + last$
    \For{$idx = 0,\ idx < sum$}
      \State $up \gets \min(idx, first, last, sum - idx)$
      \State $a[idx] \gets a[idx] + up$
    \EndFor
  \EndProcedure
\end{algorithmic}

@@
